
Create a file called \texttt{hello.sh} that contains the previous text and save it in the \texttt{Scripts/} directory.
The file extension \texttt{.sh} is technically unnecessary, but it is good practice to always include an extension.

Add executable permissions to \texttt{hello.sh}.
Run the script to verify that it worked.

The \texttt{Python/} directory contains a file called \texttt{count\_files.py}, a Python script that counts all the files within the \texttt{Shell2/} directory.
Modify this file so it can be run as a script and change the permissions of this script so the user and group can execute the script.

In addition to the \texttt{five\_secs.sh} and \texttt{ten\_secs.sh} scripts, the \texttt{Scripts/} folder contains three scripts that each take about forty-five seconds to execute.
Execute each of these commands in the background so all three are running at the same time.
While they are all running, write the output of \li{jobs} to a new file \texttt{log.txt} saved in the \texttt{Scripts/} directory.

Write a Python function \li{grep()} that accepts the name of target string and a file pattern.
Find all files in the current directory or its subdirectories that match the file pattern, then determine which ones contain the target string.
For example, \li{grep("*.py", "range(")} should search Python files for the command \li{range(}.

Validate your function by comparing it to \li{grep -lR} in the shell.

Write a Python function that accepts an integer $n$.
Search the current directory and all subdirectories for the $n$ largest files.
Return a list of filenames, in order from largest to smallest.
\\(Hint: the shell commands \li{ls -s} and \li{du} show the file size.)

The file \texttt{urls.txt} in the \texttt{Documents/} directory contains a list of URLs.
Download the files in this list using \li{wget} and move them to the \texttt{Photos/} directory.

When you finish this problem, archive and compress your entire \texttt{Shell2/} directory and save it as \texttt{ShellFinal.tar.gz}.
Include the \li{-p} flag on \li{tar} to preserve the file permissions.
\\(Hint: see the previous lab for a refresher on \li{tar}.
See also \url{https://xkcd.com/1168/}.)

Inside the \texttt{Documents/} directory, you should find a file named \texttt{files.txt}.
This file contains details on approximately one hundred files.
The different fields in the file are separated by tabs.
Using \li{awk}, \li{sort}, pipes, and redirects, write a file named \texttt{date\_modified.txt} with the following specifications:
\begin{itemize}
\item in the first column, print the date the file was modified
\item in the second column, print the name of the file
\item sort the file from newest to oldest based on the date last modified
\end{itemize}
All this can be accomplished using one command.

You will either need a partner for this problem or have access to a username on another computer.
Experiment with SSH. Verify that you can connect from a client to a host.
Copy a few files between the host and the client.
