
Write a program in which the the processes with an even rank print "Hello'' and process with an odd rank print "Goodbye.'' 
Print the process number along with the "Hello'' or "Goodbye'' 
(for example, "Goodbye from process 3'').

Write a script \texttt{passVector.py} that runs on two processes and passes an $n$ by $1$ vector of random values from one process to the other. 
Write it so that the user passes the value of $n$ in as a command-line argument.
Hint: This code will be useful in remembering how to pass command-line arguments.
\begin{lstlisting}
from sys import argv

# Pass in the first command line argument as n
n = int(argv[1])
\end{lstlisting}
\begin{lstlisting}
mpirun -n 2 python passVector.py 3
\end{lstlisting}

Write a script \texttt{passCircular.py} in which the process with rank $i$ sends a random value to the process with rank $i+1$ in the global communicator. 
The process with the highest rank will send its random value to the root process. 
Notice that we are communicating in a ring. 
For communication, only use \li{Send} and \li{Recv}. 
The program should work for any number of processes. 
Hint: Remember that \li{Send} and \li{Recv} are blocking functions but that Send. 
Does the order in which \li{Send} and \li{Recv} are called matter?

Write a script using $n$ processes to find the volume of a unit $m$-sphere testing $p$ random points in the unit $m$ dimensional box. 
All of these variables should be passed from the command line (the n processes are passed in the mpirun command as in previous problems). 
The $n$ processes should pass their individual results up to the root process, which then calculates an overall average. 
