
Solve the following convex optimization problem:
\begin{align*}
\text{minimize}\qquad &2x_1+x_2+3x_3 \\
\text{subject to}\qquad &x_1+2x_2 \geq 3 \\
	        &2x_1+10x_2+3x_3 \geq 10 \\
		&x_1 \geq 0 \\
		&x_2 \geq 0 \\
		&x_3 \geq 0
\end{align*}
Report the values for $x$ and the objective value that you obtain.
Remember to make the necessary adjustments so that all inequality constraints are $\leq$ rather than $\geq$.

Write a function called \li{l1Min()} that takes a matrix $A$ and vector $b$ as inputs, and solves the $l_1$ optimization problem. 
Report the values for $x$ and the objective value. 
Remember to first discard the unneccesary $u$ values from the minimizer.

Solve the problem by converting the last equality constraint into an inequality constraint.
Report the optimal values for $x$ and the objective function.

Find the minimizer and minimum of
\begin{equation*}
g(x,y,z) = \frac{3}{2}x^2 +2xy + xz+ 2y^2 +2yz+\frac{3}{2}z^2+3x + z
\end{equation*}
\begin{comment}
\begin{equation}
f(x) = \frac{1}{2}x\trp Qx - x\trp p
\end{equation}
where

\begin{center}
$Q =
\begin{bmatrix}
3 & 2 & 1\\
2 & 4 & 2\\
1 & 2 & 3\\
\end{bmatrix}
$
and $p =
\begin{bmatrix}
3\\
0\\
1\\
\end{bmatrix}
$
\end{center}
\end{comment}


The $l_2$ minimization problem is to
\begin{align*}
\text{minimize}\qquad &\|x\|_2\\
\text{subject to} \qquad &Ax = b.
\end{align*}

This problem is equivalent to a quadratic program, since $\|x\|_2 = x\trp x$.
Write a function called \li{l2Min()} that takes a matrix $A$ and vector $b$ as inputs and solves the $l_2$ minimization problem.
Report the values for $x$ and the objective value. 

Solve the problem above. 
Return the minimizer $x$ of $x_{i,j}$'s. 
Also return the maximum total net present value, which will be equal to the primal objective of the appropriately minimized linear function, multiplied by -1000. 
(This final multiplication after we have obtained a solution changes our answer to be a maximum, and compensates for the data being in thousands of acres).
