
Finish the following code box. You will create the function that takes as input the time, current \li{r} and \li{w} values, and all growth parameters.
\begin{lstlisting}
def predator_prey(t, y, a, alpha, c, gamma):
	'''
	Parameters:
	--------------
	t:	time variable.
	y:	an array of length len(y0) representing current wolf and rabbit populations at time t.
	a, alpha, c, gamma:	growth parameters. These are keyword arguments and can be of any length.
	
	Return:
	--------
	Return a list corresponding to the Predator-Prey model.
	'''
	pass
\end{lstlisting}

Graph the wolf-rabbit model given in \eqref{eqn: Pred-Prey}.
It should look like Figure \ref{fig: Pred-Prey}.

Consider the initial value problem
\begin{align}
	\begin{split}
\rho_F \dfrac{dF(t)}{dt} &= (1-p(t)) EB(t),\\
\rho_L \dfrac{dL(t)}{dt} &= p(t) EB(t),\\
F(0) &= F_0, \\
L(0) &= L_0.
	\end{split}\label{eqn:weight_prob1}
\end{align}
The ode is given above by the function \li{weight_odesystem}.
To solve this IVP for a specific individual we need initial conditions $F_0$ and $L_0.$
The function \li{fat_mass} given earlier calculates $F_0$ based on an individual's body weight (kg), age, height (meters), and gender.
$L_0$ is then given by $L_0 = BW - F_0$.

Suppose a 38 year old female, standing 5'8'' and weighing 160 lbs, reduces her intake from 2143 to 2025 calories/day, and increases her physical activity from little to no exercise (PAL=1.4) to exercising to 2-3 days per week (PAL=1.5).
Using \li{scipy.integrate.ode}, find and graph the solution curve for this single-stage weightloss intervention over a period of 5 years.

Note the provided code requires quantities in metric units (kilograms, meters, days) while our graph is converted to units of pounds and days.

Modify the preceding problem to handle a two stage weightloss intervention:
Suppose for the first 16 weeks intake is reduced from 2143 to 1600 calories/day and physical activity is increased from little to no exercise (PAL=1.4) to an hour of exercise 5 days per week (PAL=1.7).
The following 16 weeks intake is increased from 1600 to 2025 calories/day, and exercise is limited to only 2-3 days per week (PAL=1.5).

Find and graph the solution curve over a period of 32 weeks.

Compute the solutions $(U,V)$ of \eqref{lotka_volterra} 
% \begin{align*}
% 	\frac{dU}{d\bar{t}} &= U(1-V),\\
% 	\frac{dV}{d\bar{t}} &= \alpha V (U-1).
% \end{align*}
for initial conditions $(1/2, 3/4)$, $(1/16, 3/4)$, and $(1/40, 3/4)$.
Add these solutions to the phase portrait of the Lotka-Volterra model.
Can you see any limitations of this model?

Compute the solutions $(U,V)$ of \eqref{logistic_pred_prey}
for initial conditions $(1/3, 1/3)$ and $(1/2, 1/5)$.
Do this for parameter values $\alpha, \beta = 1, .3$ and also for values $\alpha, \beta = 1, 1.1$.
Create a phase portrait for the logistic equations using both sets of parameter values.
Remember to plot the direction field, all equilibrium points, and the orbits of the solutions.
